### 2025-04-22 paper/paper.tex
Updated Paper

Notes on this...

>>>>

Because there are several benchmarks, we will consider our model successful if any evaluation metric improves without a meaningful reducing another metric. For example, if average trip time decreases, but the other metrics remain very similar to their threshold results, we will consider the model a success.
